%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Data Scientist, Innovation Lab} % Job title
    {Allfunds} % Organization
    {Madrid, Spain} % Location
    {2018 - Present} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Developed a predictive model using \href{https://en.wikipedia.org/wiki/Random_forest}{Random Forests}, in order to profile retail costumers fund buying preferences.}
            \item {Started an experimental project for classifying share classes using \href{https://en.wikipedia.org/wiki/Natural_language_processing}{Natural Language Processing} with prospectus in PDF format.}
            \item {Defined and analysed a project to implement a company wide CRM.}
            \item {Assisted in the development of a company Datalake built using Google Cloud.}
            \item {Created a Python tool for a systematic analysis of prices.}
            \item {Developed a pipeline of internal information and advanced analytics for management reporting.}
            \item {Assisted in the development of a new cloud based rebate calculation tool.}
            \item {Created a module used to generate in the cloud the reporting of prices for internal and external users.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Teaching Assistant} % Job title
    {SAIS John Hopkins University} % Organization
    {Bologna, Italy} % Location
    {2015} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Teaching assistant in International Trade for Professor G. Plummer.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Analyst, Asset Management} % Job title
    {Banif (Santander Private Banking)} % Organization
    {Madrid, Spain} % Location
    {2009 - 2010} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Analysis of assets and portfolios for asset managers.}
            \item {Generate the weekly reporting of the fixed income portfolios.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Intern, Research} % Job title
    {Renaissance Capital} % Organization
    {London, UK} % Location
    {2008} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Research on Sub-saharan emerging markets.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Intern, Research} % Job title
    {CQS} % Organization
    {London, UK} % Location
    {2008} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Assisted portfolio managers on the analysis of firms, specially their pension liabilities.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Intern, Research} % Job title
    {ING Capital} % Organization
    {London, UK} % Location
    {2007} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Research on Easter European emerging markets and Iberian utilities.}
        \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
